%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{red}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.82]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Dániel}{Tüzes}
%\title{Resumé}                               % optional, remove / comment the line if not wanted

\address{Eötvös University, Budapest, Hungary}{}{}
\phone[mobile]{+36 70 335 8043}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{danieltuzes@gmail.com}                               % optional, remove / comment the line if not wanted
% optional, remove / comment the line if not wanted             % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Education}
\textbf{2012--2019}: Ph.D. student, Eötvös University, Budapest and Friedrich Alexander University Nuremberg. Training program: materials science and condensed matter physics with the result of summa cum laude. Thesis title: Stochastic properties of dislocation motion and rearrangement.  % arguments 3 to 6 can be left empty
\vspace{4pt}

\textbf{2007--2012}: M.Sc.\ and B.Sc.\, Eötvös University, Budapest,  training program: research physicists with the module atomic and molecular physics. Thesis title (translated): Determining polarization of dislocation ensembles.

\section{Skills}
\begin{itemize}
\item \textbf{Technical}: advanced skills in describing complex systems quantitatively with partial differential equations, simplifying the models and using proper approximations, investigating asymptotic behaviour in small and infinite large systems, gathering, evaluating and presenting data. High proficiency in maximum likelihood estimations, numeric PDE solving, equilibrium finding, linear stability analysis, Fourier-analysis, hypothesis testing and setting up different computational models.
\vspace{4pt}
\item \textbf{Human}: ability to work alone, to investigate and explore new topics self driven. Excellent and attentive group player, easily adopt roles from mindful junior employee to tough-minded intermediate leader. Proactive thinker. Good ability to tolerate extreme workload: 16hrs/day for days and 72hrs/week for weeks.
\vspace{4pt}
\item \textbf{Computer}: Intermediate level knowledge and practice in C++, used on a daily basis (classes, templates, lambdas, STL and other libraries). Intermediate level scripting practice in Gnuplot to visualize data and plot figures. Intermediate to advanced level in describing languages as LaTeX, Markdown and pandoc. Basic level practice in web technologies, like HTML, PHP, MySQL and JS.
\vspace{4pt}
\item \textbf{Language}: fluent in English (C1) and Hungarian (native), good in German (B2), passive knowledge in French (B1).
\end{itemize}

\section{Experience}
\textbf{2012--2019}: PhD Student and teacher assistant at Eötvös University, Budapest and at Friedrich-Alexander University, Nuremberg-Erlangen. Beside his studies and research, he was a lecturer in the field of Mechanics. Detailed achievements:
\begin{itemize}
\item designed and implemented a stochastic simulations to integrate non-deterministic PDEs
\item improved the efficiency of existing simulation programs by a factor of 2 using mathematical identities, and by a factor of 5 eliminating cache mismaches; implemented the a stochastic model on GPU
\item developed an impressive, sophisticated and sensitive way of investigating patterns on a 2D scalar field using Fourier-analysis
\item constructed study material from scratch; prepared setups for demonstrations and fast, live data visualization
\item initiated a new investigation topic in an international research group with an output of a PRB article
\item advanced level programming in C++: wrote code for different operating systems; used different compilers and options for different target systems and purposes; used STL intensively, along with industry-standard libraries, such as FFTW, LAPACK, Boost and CUDA; used classes, templates, lambdas
\item advanced level scripting in gnuplot, producing informative and impressive figures for data visualization
\item creating documentations in LaTeX, pandoc and different flavours of Markdown
\item intermediate level scripting in bash, regular expressions and git, basic usage of Python
\item high level of collaboration and cooperation in an international and multicultural environment, the ability to socialize and involve researchers in the workgroup
\end{itemize}
\vspace{6pt}

\textbf{7.2019 -- 9.2019}: Production leader and manager at Franz-Fertig and DUNAPOL, Buchen and Budapest.

\begin{itemize}
\item reconstructed the information technology system at DUNAPOL
\item investigated the used technology and methods how the company was supposedly working and measured the damages
\item restored the IT infrastructure, including the automated production management system, and by involving database specialist, repaired the damaged data
\item coordinated the transportation between the parent company and the subsidiary, ordered and arranged work for the employees and helped managing the acquisitions and the invoicing
\end{itemize}
\vspace{3pt}

\section{Publications, talks and presentations}
\subsection{Peer reviwed journals}
\begin{itemize}
\item Wu, RH; \textbf{Tüzes, D}; Ispanovity, PD; Groma, I; Hochrainer, T; Zaiser, M\\
	Instability of dislocation fluxes in a single slip:\\
	Deterministic and stochastic models of dislocation patterning\\
    \href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.98.054110}{PHYSICAL REVIEW B 98 : 5 Paper: 054110 , 15 p. (2018)};
    \href{https://arxiv.org/pdf/1708.05533}{arxiv PDF}
\item István, Hegyi Ádám; Dusán, Ispánovity Péter; Knapek, Michal; \textbf{Tüzes, Dániel}; Máthis, Krisztián; Chmelík, František; Dankházi, Zoltán; Varga, Gábor; Groma, István\\
    Micron-Scale Deformation: A Coupled In Situ Study of Strain Bursts and Acoustic Emission\\
    \href{https://www.cambridge.org/core/journals/microscopy-and-microanalysis/article/micronscale-deformation-a-coupled-in-situ-study-of-strain-bursts-and-acoustic-emission/DAF84F7E4CC7C2A211E39A1FFBCCB2D0}{MICROSCOPY AND MICROANALYSIS 23 : 6 pp. 1076-1081. , 6 p. (2017)};
    \href{https://arxiv.org/pdf/1604.01815}{arxiv PDF}
\item \textbf{Tüzes, D}; Ispánovity, PD; Zaiser, M\\
    Disorder is good for you: the influence of local disorder on strain localization and ductility of strain softening materials\\
    \href{https://link.springer.com/article/10.1007\%2Fs10704-017-0187-1}{INTERNATIONAL JOURNAL OF FRACTURE 205 : 2 pp. 139-150. , 12 p. (2017)};
    \href{https://arxiv.org/pdf/1604.01821}{arxiv PDF}
\item Ispánovity, PD; \textbf{Tüzes, D}; Szabó, P; Zaiser, M; Groma, I\\
    Role of weakest links and system-size scaling in multiscale modeling of stochastic plasticity\\
    \href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.95.054108}{PHYSICAL REVIEW B 95 : 5 Paper: 054108 , 13 p. (2017)};
    \href{https://arxiv.org/pdf/1604.01645}{arxiv PDF}
\item Groma, I; \textbf{Tüzes, D}; Ispánovity, PD\\
    Asymmetric X-ray line broadening caused by dislocation polarization induced by external load\\
    \href{https://www.sciencedirect.com/science/article/pii/S1359646213000110}{SCRIPTA MATERIALIA 68 : 9 pp. 755-758. , 4 p. (2013)}; \href{http://metal.elte.hu/~tuzes/docs/pre\%20AsymmetricX-ray\%20line\%20broadening\%20caused\%20by\%20dislocation\%20polarization\%20induced\%20by\%20external\%20load.pdf}{early version PDF}
\end{itemize}
    
\subsection{Books, lecture notes (Hungarian)}
\begin{itemize}
\item Analysis I - III: The official coursebook for physicists at Eötvös University
\item Mechanics practice: short summary of the lecture notes and examples for calculation 
\item Continuum mechanics practice: Introduction to deformations and strains, and examples for calculation
\item Quantum many body physics: A lecture note for MSc students. Lecturer: Gergely Szirmai and András Csordás
\end{itemize}
\vspace{6pt}
Took part in numerous prestigious international conferences and seminars, held presentations and introduced his research results using posters as well. 

\section{Scholarships and awards}
\cvitem{2018--2019}{two-year research scholarship (Hungarian Competitiveness and Excellence Program)}
\cvitem{2017/2018}{New Hungarian Excellence Program scholarship (Ministry of Human Capacities)}
\cvitem{2016/2017}{one-year research scholarship granted by Prof. Michael Zaiser}
\cvitem{2015/2016}{one-year PhD scholarship granted by BayHost}
\cvitem{2012--2017}{PhD scholarship granted by the Hungarian Ministry of Education}
\cvitem{2011/2012}{Excellence of Faculty (99.2th percentile)}
\cvitem{2011/2012}{Fellowship granted by the President of the Hungarian Republic (99.2th percentile)}
\cvitem{2009/2010}{Fellowship granted by the President of the Hungarian Republic (99.2th percentile)}
\cvitem{2008}{2nd place at \href{https://ortvay.elte.hu/main.html}{Rudolf Ortvay International Competition in Physics}}

\section{Community services and affiliations}
\cvitem{2008 -- }{Organizer in the Dürer Competition in Mathematics, Physics and Chemistry\newline
A comptetition for secondary school students, and from 2017 mentor in the \href{http://hypt.elte.hu/}{Hungarian team} of the International Young Physicists Tournament}
\cvitem{2008 -- }{Founder and maintainer of \href{http://fizweb.elte.hu/}{FizWeb}, the largest lecture note, example, exercise and book sharing platform for physicists at Eötvös University}
\cvitem{2008 -- }{Content manager and maintainer of numerous talent-related websites across Europe, like from 2013, \href{https://talentcentrebudapest.eu/}{the website of the Talent Center Budapest} (EUTCB is founded to foster and coordinate the joint European talent support activities), until 2014, \href{http://tehetsegpont.hu/}{the (Hungarian) National Talent Support Council}, from 2016, the \href{http://echa.info/}{European Council for High Ability} and the \href{http://etsn.eu/}{European Talent Support Network}}
\cvitem{2007 -- 2013}{\href{http://www.linkgroup.hu/}{Developer, content manager and maintainer of LinkGroup, the homepage of a biochemistry and network oriented research group led by \href{https://en.wikipedia.org/wiki/Peter_Csermely}{Péter Csermely}}}
\cvitem{2007 -- 2012}{Member of Bolyai College, the elite college of the Science Faculty}

\end{document}
